### 2014-01-11 docs/reports/finalreport/architecture.tex
proof reading

Interface layer is divided into two main parts. Server and client side. Server side which is denoted as Application Layer is following MVVC (Model-View, View, Controller) design model. Its main purpose is mapping Model-View objects of Interface Layer to Model objects and passing them to Business Layer and vice versa. Client-side web pages are designed based on MVVM (Model-View, View, Model) model. Tools used for developing the model are explained in Section \ref{sec:tools}.

Using AOP (Aspect-Oriented Programming), logging, error handling and security systems are designed on top of other layers.

As well as mentioned architectural patterns, following design patterns are used:
\begin{itemize}
	\item Dependency Injection and Inversion of Control implemented in Interface Layer
	\item Singleton Repository in Data Access Layer
	\item Unit of Work for handling transactions
\end{itemize}

\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.9]{figures/architecture.jpg}
\caption{System Architecture
\label{fig:architecture}}
\end{center}
\end{figure}

>>>>

Interface layer is divided into two main parts. Server- and client-side. Server-side which is denoted as Application Layer is following MVVC (Model-View, View, Controller) design model. Its main purpose is mapping Model-View objects of Interface Layer to Model objects and passing them to Business Layer and vice versa. Client-side web pages are designed based on MVVM (Model-View, View, Model) model. Tools used for developing the model are explained in Section \ref{sec:tools}.

Using AOP (Aspect-Oriented Programming), logging, error handling and security systems are developed on top of other layers.

As well as mentioned architectural design patterns, following implementation design patterns are used:
\begin{itemize}
	\item Dependency Injection and Inversion of Control implemented in Interface Layer
	\item Singleton Repository in Data Access Layer
	\item Unit of Work for handling transactions
\end{itemize}

\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.8]{figures/architecture.jpg}
\caption{System Architecture
\label{fig:architecture}}
\end{center}
\end{figure}

### 2014-01-11 docs/reports/finalreport/development.tex
proof reading

\section{Development}
\label{sec:development}
In this section, some special issues related to development of different components are described.

\subsection{Order}
Ordering page is a full client-side page following the idea of SPA (Single Page Application) using KnockoutJS and BreezeJS. By applying MVVM model, the data submitted in each step is stored in View-Model and used in the next steps. The system screen-shots of ordering process are shown in Figure\ref{fig:order-1}, Figure\ref{fig:order-2} and Figure\ref{fig:order-3}.  The payment process shown in Figure\ref{fig:order-3} is verified by a third-party service which supports different payment cards.

\subsection{Machine Learning's Data Accumulating}
In order to tackle the problem of translators ranking, a system similar to Order is designed. The system aims to accumulate data for Learning To Rank process. Based on query document, it offers three translators and stores client's (evaluator's) choice. In contrast to Order system, it eliminates the pictures and names of translators which prevents bias in final answers by estimators and puts emphasis on the presented criteria. A screen-shot of the system related to selecting the translators is shown in Figure\ref{fig:dataaccumulating}. In the next step, the data gathered by the system is applied on Learning to Rank algorithms which aim to discover the underlying pattern for proposing the best translators. The details of the project is described in seminar lecture related to the project.

\subsection{Text Matching}
Using Lucene, the documents of translators are categorized, indexed and stored based on their languages. In order to achieve the final text matching value, the similarity between each document and query document is calculated. The main problem here is the way to  aggregate result scores. As the problem is addressed in Seminar lecture, GP2\cite{gp2} algorithm is implemented.

\subsection{Translation Memory}
As it is mentioned before, the aim of Translation Memory system is helping the translators to exploit their previous-translated texts in their new translations. In order to develop the system, first HunAlign library is used for aligning the sentences of one text with the sentences of its corresponding text in the other language. While the algorithm tends to be error-prone in its basic version for complex texts, by extending dictionary and using rather simple and straightforward texts, reasonable aligned sentences were achieved. At the end, Lucene indexes the text and provides searching abilities.

\subsection{Scheduling}
The system is also designed following the SPA idea and using Java-Script libraries and Web-API. Figure\ref{fig:scheduling} depicts the schedule of an arbitrary translator.

>>>>

\section{Development}
\label{sec:development}
In this section, some special issues during the development of the platform are described.

\subsection{Order}
Order system is a full client-side web-page following the idea of SPA (Single Page Application) using KnockoutJS and BreezeJS. By applying MVVM model, the data submitted in each step is stored in View-Model and used in the next steps. The system screen-shots of ordering process are shown in Figure\ref{fig:order-1}, Figure\ref{fig:order-2} and Figure\ref{fig:order-3}.  The payment process shown in Figure\ref{fig:order-3} is verified by a third-party service which supports different payment cards.

\subsection{Machine Learning's Data Accumulating}
In order to tackle the problem of translators ranking, a system similar to Order is designed. The system aims to accumulate data for Learning To Rank process. Based on query document, it offers three translators and stores client's (evaluator's) choice. In contrast to Order system, it eliminates the pictures and names of translators which prevents bias in final answers by estimators and puts emphasis on the presented criteria. A screen-shot of the system related to selecting the translators is shown in Figure\ref{fig:dataaccumulating}. In the next step, the data gathered by the system is applied on Learning to Rank algorithms which aim to discover the underlying pattern for proposing the best translators. The details are described in seminar lecture related to the project.

\subsection{Text Matching}
Using Lucene, the documents of translators are categorized, indexed and stored based on their languages. In the next step, the similarity between each document and query document is calculated. In order to achieve the final text matching value, the calculated similarities should be aggregated. As the problem is addressed in Seminar lecture, GP2\cite{gp2} algorithm is implemented and used.

\subsection{Translation Memory}
As it is mentioned before, the aim of Translation Memory system is helping the translators to exploit their previous-translated texts in their new translations. In order to develop the system, first HunAlign library is used for aligning the sentences of one text with the sentences of its corresponding text in the other language. While the algorithm tends to be error-prone in its basic version specially for complex texts, by adding dictionaries and using just rather simple and straightforward texts, reasonable aligned sentences were achieved. At the end, Lucene indexes the text and provides searching abilities.

\subsection{Scheduling}
The system is also designed by following the SPA idea and using pure Java-Script libraries and Web-API. Figure\ref{fig:scheduling} depicts the schedule web-page interface for an arbitrary translator.

### 2014-01-11 docs/reports/finalreport/introduction.tex
proof reading

Using the platform, regardless of geographical location of translators and clients, they can communicate and proceed with translation. It aims to ease translating text to even not-so-popular languages as well as reduction of final cost.

The developed platform mainly consists of two parts. First, storing profiles of translators by providing registration as well as scheduling possibilities. Additionally, assisting them during translation process by offering a simple translation memory system. Second, providing a platform for clients to search and hire the translators and purchase the orders. Some complexities like text processing and expert ranking are tackled in the second part.

The remain of the report is organized as follows: In Section \ref{sec:scenario}, system requirements and usual scenarios are described in detail. Then in Section \ref{sec:architecture}, system architecture as well as design methods are explained. Applied tools and technologies following with a short description are introduced in Section \ref{sec:tools}. At the end in Section \ref{sec:development}, by demonstrating the final product in some screen-shots, specific issues in system development are reported.

>>>>

Using the platform, regardless of geographical location, translators and clients can communicate and proceed the translation. It aims to ease translating text to even not-so-popular languages as well as reduction of final cost.

The developed platform mainly consists of two parts. First, storing profiles of translators developed in registration and  scheduling systems. Additionally, assisting them during translation process by offering a simple translation memory system. Second, providing a platform for clients to search and hire the translators and purchase the orders.

The remain of the report is organized as follows: In Section \ref{sec:scenario}, system requirements and usual scenarios are described in detail. Then in Section \ref{sec:architecture}, system architecture as well as design methods are explained. Applied tools and technologies following with a short description are introduced in Section \ref{sec:tools}. At the end in Section \ref{sec:development}, by demonstrating the final product in some system screen-shots, specific issues in system development are reported.

### 2014-01-11 docs/reports/finalreport/problem.tex
proof reading

\section{Scenario and Requirements}
\label{sec:scenario}
In this section, first the usual system scenario is described in detail. Then, some specific requirements related to system development are specified.

@@

Using the profiles of the translators as well client's document, the value for each criteria is estimated. Cost is calculated based on price per word and the number of words in the document. Delivery time is estimated using the schedule of translator, duration per word as well as the number of words. Finally, text matching value is computed by processing the text and aggregating the similarity values between the query document and the previous-translated documents.

>>>>

\section{Scenario and Requirements}
\label{sec:scenario}
In this section, first the usual scenario of the system is described in detail. Then, some specific requirements related to system development are specified.

@@

Using the profiles of the translators as well client's document, the value for each criteria is estimated. Cost is calculated based on price per word and the number of words in the document. Delivery time is estimated using the schedule of translator, duration per word and the number of words in the document. Finally, text matching value is computed by processing the text and aggregating the similarity values between the query document and the previous-translated documents.
